Algorithm explanation

### 2013-08-22 article/algo.tex
Update pseudo-code

We implicitly assume each $\mathcal{HC}_v$ is universally quantified
by its all free variables $\textsc{FV}(\mathcal{HC}_v)$.  Without loss
of generality, we limit linear expression labels on $V_T$ vertices
with incoming edges to $1 \leq 0$, meaning $\bot$.

@@

\newcommand{\solveHorn}{\ensuremath{\mbox{\sc SolveHornGraph}}}
\newcommand{\genConstr}{\ensuremath{\mbox{\sc GenerateConstraint}}}

\begin{algorithm}
\caption{$ \solveHorn (G) $}\label{alg:solveHorn}
\begin{algorithmic}
\STATE {$v_\bot \gets $ the root node of $G$}
\STATE {$visited \gets \left\lbrace v_\bot \right\rbrace$}

\STATE {$C \gets \genConstr (v_\bot, visited)$}
\STATE {$c_{v_\bot} \gets C(v_\bot)$}
\IF {$c_{v_\bot}$ is satisfiable}
  \IF {$visited$ contains all predicate variable vertices}
    \STATE {$visited \gets a$}
    \COMMENT {build solution}
  \ELSE
    \STATE {$visited \gets a$}
  \ENDIF
\ELSE
  \STATE {$\mathcal{UC} \gets $ unsatisfiable core for $c_{v_\bot}$}
\ENDIF
\end{algorithmic}
\end{algorithm}

@@

The construction of the algorithm is two fold.
\begin{itemize}
\item \textbf{Iterative Constraint Building} The process starts from
  generating the weakest constraint that the graph allows and
  iteratively strengthen a constraint until the strongest one.
\item \textbf{Graph Restructuring} If the constraint become
  unsatisfiable during the iteration, restructure the input Horn graph
  to enlarge the solution template.
\end{itemize}

@@

For each predicate variable vertex, build a linear constraint
  that parameters in predicate variable templates must satisfy.

$\genConstr$ procedure produces the constraint for all vertices

In this algorithm, vertices with a predicate variable label must have
a simple solution assignment.

>>>>

We implicitly assume each $\mathcal{HC}_v$ is universally quantified
by its all free variables $\textsc{FV}(\mathcal{HC}_v)$.  Without loss
of generality, we assume the existence of the root vertex $v_\bot \in
V_T$ with linear expression labels $1 \leq 0$, meaning $\bot$. We also
assume that other vertices with linear expression labels have no
incoming edges to them.

@@

\newcommand{\solveHorn}{\ensuremath{\mbox{\sc SolveHornGraph}}}
\newcommand{\genConstr}{\ensuremath{\mbox{\sc GenerateConstraint}}}
\newcommand{\splitGraph}{\ensuremath{\mbox{\sc RestructureGraph}}}

\begin{algorithm}
\caption{$ \solveHorn (G) $}\label{alg:solveHorn}
\begin{algorithmic}
\STATE {$v_\bot \gets $ the root node of $G$}
\STATE {$V \gets \left\lbrace v_\bot \right\rbrace$}
\REPEAT
  \STATE {$C \gets \genConstr (v_\bot, V)$}
  \STATE {$c_{v_\bot} \gets C(v_\bot)$}
  \STATE {Evaluate satisfiability of $c_{v_\bot}$}
  \IF {$c_{v_\bot}$ is unsatisfiable}
    \STATE {$\mathcal{UC} \gets $ unsatisfiable core for $c_{v_\bot}$}
    \STATE {$G \gets \splitGraph (G, \mathcal{UC})$}
    \STATE {$V \gets \left\lbrace v_\bot \right\rbrace$}
  \ELSE
    \STATE {Enlarge $V$}
    \STATE {$m \gets $ one model of $c_{v_\bot}$}
  \ENDIF
\UNTIL {$V$ contains all predicate variable vertices}
\STATE {Build solution by $m$}
\end{algorithmic}
\end{algorithm}

@@

The construction of the algorithm is in two fold.
\begin{itemize}
\item \textbf{Iterative Constraint Building} The process starts from
  generating the weakest constraint that the graph allows and
  iteratively strengthen a constraint until the strongest one.
\item \textbf{Graph Restructuring} If the constraint become
  unsatisfiable during the iteration, restructure the input Horn graph
  to enlarge the solution template.
\end{itemize}
This algorithm enables a solution to be build as simple as possible.

@@

For each predicate variable vertex, build a linear constraint that
parameters in predicate variable templates must satisfy.  The process
is equivalent to generate a linear constraint in interpolation.

$\genConstr$ procedure produces the constraint for all vertices. The
constraints are first built the weakest so that the disjunctiveness of
whole solution template is fixed first.
